Typed Interactions for NLU in Opal

### 2017-12-13 paper.tex
Added a paragraph to the conclusion
(It's a little dramatic)

>>>>

As we move towards a future where the majority of our interactions with
computers happen via human language, projects like this will become more and
more important. It may be that the approach put forth in the paper paves the way
for safe, correct applications that work with NLU. However, even if a different
approach wins out, it is almost certain that safe interfaces to NLU engines will
eventually become wide-spread. Just as companies have tended to favor strongly
typed language for applications where correctness matters, programmers working
with NLU will eventually see the need to do so in a principled way.
